Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
SR by hand

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum}

#
# List of all courses
course_all <- unique(d_transactions$taken_PF_HL$item)

@@

  group_by(
    sequenceID,
    eventID
    ) %>%
  summarize(
    course_current = list(
      unique(item_PF)
      )
    ) %>%

  group_by(
    sequenceID
    ) %>%
  mutate(
    course_past = Reduce(
      f = c, 
      x = course_current, 
      accumulate = TRUE
      ) %>%
      lag(
        default = as.character(NA)
        )
    ) %>%

  rowwise %>% # equivalent to "group by row"
  mutate(
    course_so_far     = list(union  (course_past, course_current)),
    course_not_so_far = list(setdiff(course_all , course_so_far ))
    ) %>%
  ungroup

@@

}
```
###Apply Functions
We apply make_AR to get different sets of rules:

#### take -> take
```{r AR take}
AR <- list()

@@

#### fail -> fail
```{r AR fail}
AR$PF <- transactions$PF %>%

@@

#### low grade -> low grade
```{r AR low}
AR$HL <- transactions$HL %>%

@@

#### not take -> fail
```{r AR TPF}
AR$TPF <- transactions$TPF %>%

@@

#### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@

### Editing AR
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_AR}
edit_rules <- function(AR){

@@

# Remove objects
rm(
  my_apriori, make_AR,
  AR, transaction
  )

## Sequence Rules
### Functions
The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
```{r my_cspade function}
my_cspade <- function(data){

@@

}
```
The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
```{r my_ruleInduction}
my_ruleInduction <- function(rules){

@@

}
```
We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
```{r make_SR}
make_SR <- function(data, data_support, type_rule){

@@

}
```
###Apply Functions
We apply make_SR to get different types of sequential rules:
#### take -> take
```{r SR taken}
SR <- list()

@@

#### fail -> fail
```{r SR PF}
SR$PF <- sequences$PF %>%

@@

#### low grade -> low grade
```{r SR HL, cache = TRUE}
SR$HL <- sequences$HL %>%

@@

#### not take -> fail
```{r SR TPF, eval = FALSE}

#
# SR by hand

# rhs = current course
d_transcript_cum_current <- d_transcript_cum %>%
  unnest(
    course_current,
    .drop = FALSE
    ) %>%
  rename(
    rhs = course_current
    )

# lhs = course not so far
d_transcript_cum_current %>%
  unnest(
    course_not_so_far,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_not_so_far
    ) %>%
  count(
    lhs, 
    rhs,
    sort = TRUE
    ) %>%
  filter(str_detect(rhs, "fail"))
```

#### grade less than or equal to x -> grade less than or equal to 6
```{r SR G, cache = TRUE}
SR$G <- sequences$G %>%

>>>>

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum}
#
# List of all courses
course_all <- unique(d_transactions$taken_PF_HL$item)

@@

  # item_take
  mutate(
    item_take = paste(item, "take", sep = "_")
  ) %>%

  # course current
  group_by(
    sequenceID,
    eventID
    ) %>%
  summarize_at(
    c("item", "item_take", "item_PF", "item_HL"),
    function(x) list(unique(x))
    ) %>%
  ungroup %>%

  # course current all
  rowwise %>%
  mutate(
    course_current = list(c(item, item_take, item_PF, item_HL))
    ) %>%
  ungroup %>%

  # course past
  group_by(
    sequenceID
    ) %>%
  mutate(
    course_past = Reduce(
      f = c,
      x = course_current,
      accumulate = TRUE
      ) %>%
      lag(
        default = as.character(NA)
        )
    ) %>%
  ungroup %>%

  # course so far, course not so far
  rowwise %>%
  mutate(
    course_past_current = list(union  (course_past, course_current      )),
    course_not_yet      = list(setdiff(course_all , course_past_current )),
    course_not_yet      = list(paste(course_not_yet, "not", sep = "_"   )),
    course_so_far       = list(union  (course_past, course_not_yet))
    ) %>%
  ungroup %>%

  # lhs: past, rhs: present
  select(
    sequenceID,
    lhs = course_so_far,
    rhs = course_current
  )

@@

### take -> take
```{r AR take}
AR <- list()

@@

### fail -> fail
```{r AR fail}
AR$PF <- transactions$PF %>%

@@

### low grade -> low grade
```{r AR low}
AR$HL <- transactions$HL %>%

@@

### not take -> fail
```{r AR TPF}
AR$TPF <- transactions$TPF %>%

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@

### Editing AR
```{r edit_AR}
edit_rules <- function(AR){

@@

# Remove objects
rm(
  my_apriori, make_AR,
  AR, transaction
  )
```

## Sequence Rules
### Functions

```{r my_cspade function}
my_cspade <- function(data){

@@

```{r my_ruleInduction}
my_ruleInduction <- function(rules){

@@

```{r make_SR}
make_SR <- function(data, data_support, type_rule){

@@

### take -> take
```{r SR taken}
SR <- list()

@@

### fail -> fail
```{r SR PF}
SR$PF <- sequences$PF %>%

@@

### low grade -> low grade
```{r SR HL, cache = TRUE}
SR$HL <- sequences$HL %>%

@@

### not take -> fail
```{r SR TPF, eval = FALSE}
#
# SR

x <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "low")
    ) %>%

  # lhs
  unnest(
    lhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(lhs, "not")
    ) %>%

  # support
  count(
    lhs,
    rhs
    )
```

### grade less than or equal to x -> grade less than or equal to 6
```{r SR G, cache = TRUE}
SR$G <- sequences$G %>%
